\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2020-08-27 sections/introduction.tex
Updates from Overleaf

 This wealth of information on the composition and functions of a community at different times and under different environmental conditions has the potential to help us understand how communities assemble and operate.
 A powerful tool for translating microbiome data into knowledge is the construction of possible inter-dependence networks across species.
 The importance of these networks of relationships is two fold: first, such networks can serve as maps that help identify hubs of keystone species \cite{Menon2018,Rottjers2018}, or basic microbiome changes that occur as a consequence of environmental perturbations or underlying host conditions \cite{Gilbert2016}; second, networks of inter-dependencies can serve as a key bridge towards building mechanistic models of microbial communities, greatly enhancing our capacity to understand and control them.
 For example, multiple studies have shown the importance of specific microbial interactions in the healthy microbiome \cite{Lloyd-Price2016} and others have shown how changes in these interactions can lead to dysbiosis \cite{Wang2017,Gilbert2016,Belizario2015}.
 In the context of terrestrial biogeochemistry, co-occurrence networks have proposed as a valuable approach towards reconstructing the processes leading to microbiome assembly [REF Fierer], and understanding the response of microbial communities to environmental perturbations [REF].

 Direct high-throughput measurement of interactions, e.g. through co-culture microdroplet experiments [REF Blainey], or spatial visualization of natural communities [REF Borisy] is possible, but it requires specific technological capabilities, and has not been used very extensively yet.
 In parallel, sequencing data across multiple samples can be used for estimating co-occurrence relationships between taxa.
 While the the relationship between directly measured interactions and statistically inferred co-occurrence is still poorly understood \cite{Zuniga2017}, a significant amount of effort has gone into estimating correlations from large microbiome sequence datasets.
 Co-occurrence networks have microbial taxa as nodes, and edges that represent the frequent co-occurrence (or negative correlations) across different datasets.

One of the most frequently used avenues for inferring co-occurrence networks is the parsing and analysis of 16S sequencing data [REF]. A large number of software tools and pipelines have been developed to analyze 16S sequencing data, often focused on addressing the many known limitations of this methodology, including resolution, sequencing depth, compositional nature, sequencing errors and copy number variations [REF]. Popular methods for different phases of the analysis of 16S data include tools for: (i) denoising and clustering sequencing reads \cite{Caporaso2010,Callahan2016}; (ii) assigning taxonomy to the reads \cite{DeSantis2006,Quast2012}; (iii) processing and transforming the taxonomy count matrices \cite{Weiss2015}; and (iv) inferring the co-occurrence network \cite{Cougoul2019,Kurtz2015}.
Different specific algorithms are often aggregated into popular platforms (like MG-RAST \cite{Keegan2016}, Qiita \cite{qiita}) and packages (such as QIIME \cite{Caporaso2010}) that provide pipelines for 16S data analysis.
The different methods and tools developed to solve issues arising in 16S analysis can lead to vastly different inferences of community compositions and co-occurrence networks \cite{Golob2017,Weiss2016}, making it difficult to reliably compare networks across different publications and studies.
 This is partially due to the fact that existing platforms are typically focused on \ac{otu} generation and not on the effects of upstream statistical methods on the inferred co-occurrence networks.
 Furthermore, no organized framework currently exist to systematically analyze and compare existing components of the data-analysis from amplicons to networks.
  More broadly, given the lack of comprehensive comparisons between directly observed microbial interactions (e.g. from co-culture experiments) and co-occurrence networks, there is no straightforward way to determine which set of tools or methods generate the most accurate networks.

>>>>

 This wealth of information on the composition and functions of a community at different times and under different environmental conditions has the potential to help us understand how communities assemble and operate.
 A powerful tool for translating microbiome data into knowledge is the construction of possible inter-dependence networks across species.
 The importance of these networks of relationships is two fold: first, such networks can serve as maps that help identify hubs of keystone species \cite{Menon2018,Rottjers2018}, or basic microbiome changes that occur as a consequence of environmental perturbations or underlying host conditions \cite{Gilbert2016}; second, networks of inter-dependencies can serve as a key bridge towards building mechanistic models of microbial communities, greatly enhancing our capacity to understand and control them.
 For example, multiple studies have shown the importance of specific microbial interactions in the healthy microbiome \cite{Lloyd-Price2016} and others have shown how changes in these interactions can lead to dysbiosis \cite{Wang2017,Gilbert2016,Belizario2015}.
 In the context of terrestrial biogeochemistry, co-occurrence networks have proposed as a valuable approach towards reconstructing the processes leading to microbiome assembly \cite{Fierer2017}, and understanding the response of microbial communities to environmental perturbations \cite{Jiao2019}.

 Direct high-throughput measurement of interactions, e.g. through co-culture microdroplet experiments \cite{Hsu2019,Jian2020}, or spatial visualization of natural communities \cite{Wilbert2020} is possible, but it requires specific technological capabilities, and has not been used very extensively yet.
 In parallel, sequencing data across multiple samples can be used for estimating co-occurrence relationships between taxa.
 While the the relationship between directly measured interactions and statistically inferred co-occurrence is still poorly understood \cite{Zuniga2017}, a significant amount of effort has gone into estimating correlations from large microbiome sequence datasets.
 Co-occurrence networks have microbial taxa as nodes, and edges that represent the frequent co-occurrence (or negative correlations) across different datasets.

One of the most frequently used avenues for inferring co-occurrence networks is the parsing and analysis of 16S sequencing data \cite{Rottjers2018,Friedman2012}. A large number of software tools and pipelines have been developed to analyze 16S sequencing data, often focused on addressing the many known limitations of this methodology, including resolution, sequencing depth, compositional nature, sequencing errors and copy number variations \cite{Bharti2019,Pollock2018}. Popular methods for different phases of the analysis of 16S data include tools for: (i) denoising and clustering sequencing reads \cite{Caporaso2010,Callahan2016}; (ii) assigning taxonomy to the reads \cite{DeSantis2006,Quast2012}; (iii) processing and transforming the taxonomy count matrices \cite{Weiss2015}; and (iv) inferring the co-occurrence network \cite{Cougoul2019,Kurtz2015}.
Different specific algorithms are often aggregated into popular platforms (like MG-RAST \cite{Keegan2016}, Qiita \cite{qiita}) and packages (such as QIIME \cite{Caporaso2010}) that provide pipelines for 16S data analysis.
The different methods and tools developed to solve issues arising in 16S analysis can lead to vastly different inferences of community compositions and co-occurrence networks \cite{Golob2017,Weiss2016}, making it difficult to reliably compare networks across different publications and studies.
 This is partially due to the fact that existing platforms are typically focused on \ac{otu} generation and not on the effects of upstream statistical methods on the inferred co-occurrence networks.
 Furthermore, no organized framework currently exist to systematically analyze and compare existing components of the data-analysis from amplicons to networks.
  More broadly, given the lack of comprehensive comparisons between directly observed microbial interactions (e.g. from co-culture experiments) and co-occurrence networks, there is no straightforward way to determine which set of tools or methods generate the most accurate networks.
